---
title: "Period 3"
---

```{r}
library(dplyr)
library(igraph)
library(tidygraph)
library(sf)
library(ggplot2)
library(sp)
library(STNet)
library(raster)
library(fasterize)
library(here)
library(gridExtra)
library(nngeo)
library(scales)
library(cowplot)
```

# Objectives:

-  Update the predictions for effectiveness of the fences implemented with or without the increased hunting pressure.  
-  How likely the epidemic is to fade in the coming four months (day 240)?
-  Are there any risks to consider for long term?
  -  Second wave
  -  Endemicity in wild boar  
  -  Others?
-  Suggestions to limit the risk
-  Should control measures be lifted after 240 days?

Deadline: **January 13th, 2021**.

# Data overview:

```{r Create hexagonal grid}
# Get the CRS that we will use for the data
projCRS <- shapefile(here("Data/InitialData/Island_ADMIN.shp")) %>% crs()

# Resolution of the grid:
HxRes <- 5e3

# Read the shapefile
Is <- sf::read_sf(here("Data/InitialData/Island_ADMIN.shp"))

# explicitly indicate the CRS in sp format to avoid future issues when converting between formats
st_crs(Is) <- projCRS

# Convert to a field
Border <- as(raster::extent(Is), "SpatialPolygons") %>%
  sf::st_as_sf()
st_crs(Border) <- st_crs(Is)

# Create the grid
# Cells that overlapped two different polygons (admin) were duplicated, edited the function to simplify the original shapefile.
new_hex_grid = function(cellsize, border, orig_shp) {
  # cellsize = HxRes; border = Border; orig_shp = Is
  simple_shp <- orig_shp %>%
    mutate(i = 1) %>% count(i)
  
  DFsp <- border %>% as("Spatial")
  HexPts <- sp::spsample(DFsp, type = "hexagonal", offset = c(0, 
    0), cellsize = cellsize)
  HexPols <- sp::HexPoints2SpatialPolygons(HexPts)
  HexPols_sf = st_as_sf(HexPols)
  
  hexgrid = st_join(HexPols_sf, simple_shp) %>%
    filter(!is.na(n)) %>%
    # rename(orig_shp_ID = ID) %>%
    mutate(idhex = as.character(seq_len(nrow(.)))) %>%
    dplyr::select(idhex)
  
  return(hexgrid)
}

BHx <- new_hex_grid(cellsize = HxRes, border = Border, orig_shp = Is)
# st_write(BHx, '../../../Data/Period_2/out/BHx.shp')

if(FALSE){
  # Older version, which returns hexgrids for entire border extent,
  #   instead of just for the polygon area
  BHx <- STNet::HexGrid(cellsize = HxRes, Shp = Border)
  plot(BHx)
}

# This plot doesnt work anymore, I dont think we need it
if(FALSE){
  ggplot() +
    # geom_sf(data = border) +
    geom_sf(data = BHx, aes(fill = orig_shp_ID, col = orig_shp_ID), alpha = 0.7) +
    geom_sf(data = Is, aes(fill = ID), col = "grey35", alpha = 0.5) +
    theme_void()
  
  # Note: the ID's aren't sequential - they're like that from the Island data
  BHx$orig_shp_ID = NULL # don't need the orig IDs going forward
}
```

## Herds.

```{r}
herds <- read.csv(here("Data/Period_3/herds_day_110.csv"))
######## Summarize herds ########
herds <- herds %>%
  mutate(N=1) %>%
  tidyr::spread(production, N) %>% # Convert from long to wide for farm types
  replace(., is.na(.), 0) # Replace NAs with 0

herdsSp <- herds %>%
  sf::st_as_sf(coords = c("X", "Y"), crs = st_crs(Is)) %>%
  st_join(BHx)

herdsHx <- herdsSp %>%
  mutate(N = 1) %>%
  group_by(idhex) %>%
  summarise_at(.vars = c('N', 'size', 'is_outdoor', 'is_commercial', 'multisite', 'B', 'BF', 'F'), .funs = sum) %>%
  mutate(density = size/ N) %>% # expected animals per farm
  data.frame() %>%
  dplyr::select(-geometry) %>%
  rename(Farms = N, Pop = size)

Hx <- BHx %>%
  left_join(herdsHx)
```

## Movements

```{r}
Mov <- read.csv(here("Data/Period_3/moves_Players_day_110.csv"))

MovHx <- Mov %>%
  left_join(data.frame(herdsSp)[c('population_id', 'idhex')], by = c('source' = 'population_id')) %>%
  rename(sourceHx = idhex) %>%
  left_join(data.frame(herdsSp)[c('population_id', 'idhex')], by = c('dest' = 'population_id')) %>%
  rename(destHx = idhex) %>%
  mutate_at(.vars = c('sourceHx', 'destHx'), .funs = as.character)

# How long was the period observed?
period_t <- MovHx %>%
  count(date) %>%
  nrow()

# Get the probability of movements (long distance) and loops (short distance/internals)
MovpHx <- MovHx %>%
  mutate(Mov = 1, loop = ifelse(sourceHx == destHx, 1, 0)) %>%
  group_by(sourceHx) %>%
  summarise(Mov = sum(Mov, ma.rm = T), loop = sum(loop), E_animals = median(qty)) %>%
  mutate(Mov = Mov/period_t, loop = loop/period_t)

# join with the herds dataset
Hx <- Hx %>%
  left_join(MovpHx, by = c('idhex' = 'sourceHx'))

# Create table for the movement destinations
MovHx_c <- lapply(unique(MovHx$sourceHx), function(x){
  Nbs <- MovHx %>%
    filter(sourceHx == x) %>%
    pull(destHx) %>%
    paste(collapse = ' ')
  data.frame(sourceHx = x, Nbs)
}) %>%
  do.call(rbind, .)

write.csv(MovHx_c, here(paste0("Data/Period_3/out/MovHx_c-", HxRes ,".csv")), row.names = F, quote = F)

MovHx %>%
  mutate(ID = 1:n(), sourceHx = as.integer(sourceHx), destHx = as.integer(destHx)) %>%
  dplyr::select(ID, sourceHx, destHx) %>%
  # slice(1:200) %>%
  write.csv(., here(paste0("Data/Period_3/out/MovHx-", HxRes, ".csv")), row.names = FALSE, quote = FALSE)
```

# wild boars

```{r, cache = TRUE}
hunting <- read.csv(here("Data/InitialData/WB_HuntingBag.csv"), sep = ";")

Is <- Is %>% 
  mutate(ID = as.integer(as.character(ID)), area = st_area(.)) %>%
  left_join(hunting, by = c("ID" = "ADM")) %>%
  mutate(WB_dens = HB_2019/area) 
# Create an empty raster (increaseing the ncol and nrow will give us a better resolution, but will also increase the computation time)
r <- raster(ncol = 1000, nrow = 1000)
crs(r) <- crs(Is)
# Set the extent same as the shapefile
extent(r) <- extent(Is)

WBr <- fasterize::fasterize(sf = Is, raster = r, field = "WB_dens", fun = "sum")
# Specify the CRS
crs(WBr) <- projCRS

Vals <- lapply(seq_len(nrow(Hx)), function(x){
  mean(raster::extract(WBr, Hx[x,])[[1]], na.rm = TRUE)
})

Hx <- Hx %>%
  mutate(WBd = do.call(rbind, Vals), E_WB = (WBd * HxRes) * 1000)

# Compare plots
Hx %>%
  ggplot()+
  geom_sf(aes(fill = E_WB))

  
plot(WBr)
```

# Land cover

```{r}
LC <- st_read(here("Data/Shapefiles/Island_LANDCOVER.shp"))
```

```{r}
# Recode the land cover levels to manipulate later
LC <- LC %>%
  mutate(LC = recode(LANDCOVER, Agricultural = 1, Forest = 10, Urban = 100))
```

We will put all the information in a raster so we can then extract and summarize the values per hexagon

```{r}
# Use the function fasterize to sum the number of N over each pixel of our raster
LCr <- fasterize::fasterize(sf = LC, raster = r, field = "LC", fun = "sum")
# Specify the CRS
crs(LCr) <- projCRS # NR: for me the crs' were already identical
# Get the unique values to see if worked
unique(values(LCr))
```
  
  
Some of the values are not the ones we recoded for (there might be some overlapping of the values due to the resolution used), we can see that the unexpected numbers are just sums of two of the same type, so we will just replace those:

```{r}
# Replace NAs for 0s
LCr[is.na(LCr[])] <- 0
# Replace overlapping raster cells
LCr[(LCr[] > 1 & LCr[] < 9)] <- 1
LCr[(LCr[] > 10 & LCr[] < 90)] <- 10
LCr[(LCr[] > 100 & LCr[] < 900)] <- 100
# Plot the raster
plot(LCr)
```

Now we will summarize the values per hexagon

```{r, cache = TRUE}
# Updated this code with newer version below
if(FALSE){
  # Create empty vectors
  A_vals <- vector()
  F_vals <- vector() 
  U_vals <- vector()
  # Make a loop that will run for each hexagon
  for(i in 1:nrow(Hx)){
    # Get the values for each haxagon
    Vals <- raster::extract(LCr, Hx[i,])
    # get the proportion of each type of land cover
    AVals_i <- length(Vals[[1]][Vals[[1]] == 1]) / length(Vals[[1]])
    FVals_i <- length(Vals[[1]][Vals[[1]] == 10]) / length(Vals[[1]])
    UVals_i <- length(Vals[[1]][Vals[[1]] == 100]) / length(Vals[[1]])
    # create vectors with the values:
    A_vals <- c(A_vals, AVals_i)
    F_vals <- c(F_vals, FVals_i)
    U_vals <- c(U_vals, UVals_i)
  }
}

# Make a loop that will run for each hexagon
Vals_l = lapply(seq_len(nrow(Hx)), function(n, Hx, LCr) {
  Vals <- raster::extract(LCr, Hx[n, ])[[1]]
}, Hx, LCr)

# get the proportion of each type of land cover
A_vals = sapply(Vals_l, function(Vals) {
  sum(Vals == 1) / length(Vals)
})

F_vals = sapply(Vals_l, function(Vals) {
  sum(Vals == 10) / length(Vals)
})

U_vals = sapply(Vals_l, function(Vals) {
  sum(Vals == 100) / length(Vals)
})

# Add the values to the Spatial hexagon layer:
Hx <- Hx %>%
  mutate(Agricultural = A_vals, Forest = F_vals, Urban = U_vals)

# Plots
p_urban = Hx %>%
  ggplot()+
  geom_sf(aes(fill = Urban)) +
  scale_fill_gradient(limits = c(0, 1), high = "yellow")

p_forest = Hx %>%
  ggplot()+
  geom_sf(aes(fill = Forest)) +
  scale_fill_gradient(limits = c(0, 1), high = "green")

p_agricultural = Hx %>%
  ggplot()+
  geom_sf(aes(fill = Agricultural)) +
  scale_fill_gradient(limits = c(0, 1), high = "purple")

gridExtra::grid.arrange(p_urban, p_forest, p_agricultural, ncol = 3)
```
```{r}
Hx0 <- Hx
```

```{r}
# Export the grid before the cases.
# st_write(Hx, "../../../Data/Period_3/out/Hx_LC.shp")
Hx <- st_read("../../../Data/Period_3/out/Hx_LC.shp")
```



# Cases

Cases comes in two datasets, one for positives and other for negative tests.  
```{r}
# Variable to spread categorical variables
unfold <- function(Dat, Var){
  Dat %>% mutate(N=1) %>% tidyr::spread(eval(parse(text = Var)), N, fill = 0)
}
```


```{r}
TSp_sf2 <- read.csv("../../../Data/Period_3/TimeSeries_day_110_all.csv") %>%
  unfold(., "HOST") %>%
  mutate(Positive = 1) %>%
  filter(DATE.CONF > 80) %>%
  st_as_sf(., coords = c("X", "Y"), crs = st_crs(BHx))

# TSp_sf2 %>%
#   st_write("../../../Data/Period_2/out/TSsp.shp")

TSp_sf2 %>%
  data.frame() %>%
  # filter(DATE.CONF > 80) %>%
  # count(DET)
  # mutate()
  arrange(desc(`pig.herd`))
```

```{r}
TSHx <- TSp_sf2 %>%
  st_join(BHx)

## Join with the Hx
TSp_s <- TSp_sf2 %>%
  st_join(BHx) %>%
  data.frame() %>%
  group_by(idhex) %>%
  summarise(cases = sum(Positive), wb_cases = sum(wild.boar), ph_cases = sum(pig.herd))

# Join to the Hx Shapefile
Hx <- Hx %>%
  # dplyr::select(-c(cases, wb_cass, ph_cass)) %>%
  left_join(TSp_s, by = 'idhex')
```





```{r}
# For some reason the original st_join method was giving two hex joins for some points
# Possibly due to points being on the hexagon borders?
# Ref:  https://stackoverflow.com/questions/51381900/r-overlay-points-and-polygons-with-a-certain-degree-of-tolerance

if(FALSE){
  # Read the positives
TSp <- read.csv("../../../Data/Period_1/TimeSeries_day_50.csv") %>% 
  unfold(., "HOST") %>%
  mutate(Positive = 1) %>%
  st_as_sf(., coords = c("X", "Y"), crs = st_crs(BHx)) %>%
  st_join(BHx) %>% data.frame() %>% 
  group_by(idhex, DATE.CONF) %>%
  summarise(cases = sum(Positive), wb_cases = sum(wild.boar), ph_cases = sum(pig.herd))
}

# Read the positives
TSp_sf <- read.csv(here("Data/Period_3/TimeSeries_day_110.csv")) %>% 
  unfold(., "HOST") %>%
  mutate(Positive = 1) %>%
  st_as_sf(., coords = c("X", "Y"), crs = st_crs(BHx))

TSp = st_join(TSp_sf, BHx, join = st_nn) %>%
  data.frame() %>% 
  group_by(idhex, DATE.CONF) %>%
  summarise(cases = sum(Positive), wb_cases = sum(wild.boar), ph_cases = sum(pig.herd))

# How does the cumulative number of cases per grid looks like?
TSp %>%
  dplyr::filter(!is.na(DATE.CONF)) %>%
  group_by(idhex) %>%
  mutate(cases_cum = cumsum(cases)) %>%
  ggplot() +
  geom_line(aes(x=DATE.CONF, y=cases_cum, col = idhex))

ggplot() +
    geom_sf(data = BHx, fill = "grey") +
    geom_sf(data = TSp_sf, col = "yellow", size = 0.5)
```

```{r}
# Add the number of cases to the data
TSp_s <- TSp %>%
  group_by(idhex) %>%
  summarise_at(.vars = c('cases', 'wb_cases', 'ph_cases'), .funs = sum)
# Join to the Hx Shapefile
Hx <- Hx %>%
  left_join(TSp_s, by = 'idhex')
# Hx %>%
#   data.frame() %>%
#   arrange(desc(wb_cases))
```

```{r, cache = TRUE}
# Now read the negatives
TSn_sf <- read.csv(here("Data/Period_1/TimeSeries_hunt_negative_test_day_50.csv")) %>%
  unfold(., "HOST") %>%
  mutate(Negative = 1) %>%
  st_as_sf(., coords = c("X", "Y"), crs = st_crs(BHx))

TSn = st_join(TSn_sf, BHx, join = st_nn) %>%
  data.frame() %>% 
  group_by(idhex, DATE.CONF) %>%
  summarise(negatives = sum(Negative), wb_cases = sum(wild.boar), ph_cases = 0)
# The above is hunting data only, with no pig herd cases. Hence setting it to 0.


ggplot() +
  geom_sf(data = BHx, fill = "grey") +
  geom_sf(data = TSn_sf, col = "blue", size = 0.5) +
  geom_sf(data = TSp_sf, col = "orange", size = 0.5) +
  theme_void()


if(FALSE){
  # Now read the negatives
  TSn <- read.csv(here("Data/Period_1/TimeSeries_hunt_negative_test_day_50.csv")) %>%
    unfold(., "HOST") %>%
    mutate(Test = 0) %>%
    st_as_sf(., coords = c("X", "Y"), crs = st_crs(BHx)) %>%
    st_join(BHx) %>% data.frame() %>%
    group_by(idhex) %>%
    summarise(tests = sum(Test), wb_tests = sum(wild.boar)) 
}


HxDF <- Hx %>%
  filter(!is.na(Pop)) %>%
  data.frame()

HxDF %>%
  arrange(desc(cases))


HxDF %>%
  # mutate(wb_bool = ifelse(Result != 0 & wild.boar != 0, 1, 0)) %>% # For wild boars
  mutate(wb_bool = ifelse(cases != 0 & ph_cases != 0, 1, 0)) %>% # For pig herds
  group_by(wb_bool) %>%
  summarise_at(.vars = c('is_outdoor', 'is_commercial', 'multisite', 'B', 'BF', 'F', 'density', 'Agricultural', 'Forest', 'Urban', 'E_WB'), .funs = mean)

# I exchanged Result for cases and also ph_cases for pig.herd above.
# Not sure if the above was what was aimed at though

if(FALSE){
  HxDF %>%
    # mutate(wb_bool = ifelse(Result != 0 & wild.boar != 0, 1, 0)) %>% # For wild boars
    mutate(wb_bool = ifelse(Result != 0 & pig.herd != 0, 1, 0)) %>% # For pig herds
    group_by(wb_bool) %>%
    summarise_at(.vars = c('is_outdoor', 'is_commercial', 'multisite', 'B', 'BF', 'F', 'density', 'Agricultural', 'Forest', 'Urban', 'E_WB'), .funs = mean)
}

```

```{r}
# There's no TS defined in the previous code
if(FALSE){
TS %>%
  tidyr::spread(data = ., HOST, Result)

HxDF %>%
  filter(pig.herd !=0)
}

```

# Weighted linear combination

```{r}
HxDF %>%
  mutate(density_s = scales::rescale(x = density, to = c(0.2,0.6))) %>%
  ggplot() + geom_histogram(aes(density_s))
```

Variables:

-   DET: detection method:

    -   PS- Passive surveillance.
    -   RZ- Detection in a site from surveillance or protection zone.
    -   TR- Detection via tracing.
    -   AS- Wild boar carcass via active searching
    -   NAS- non-infected carcass via active searching.
    -   PT- detection of in a hunted boar.
    -   NT- non-infected hunted boar.

```{r Export the data}
# Export data:
Hxe <- Hx %>%
  filter(!is.na(Pop) | !is.na(E_WB)) %>% # Select only the cells with a WB or PH population
  mutate(Farms = ifelse(is.na(Farms), 1e-6, Farms), # If there is no PH pop, set a very small number for the model
    density_s = scales::rescale(x = density, to = c(0.2,0.6)), # Score based on the density
     WB_score = scales::rescale(x = Forest, to = c(0,.5)) + # score based on the forest cover and EWb density
           scales::rescale(x = WBd, to = c(0,.5)), # score based on the forest cover and EWb density
          outdoor = ifelse(is.na(is_otdr), 0, is_otdr),
    outdoor = scales::rescale(outdoor, c(0.01, 0.5)),
    WBd = scales::rescale(WBd, to = c(0.05, 0.25)),) 

Hxe %>% dplyr::select(idhex, is_otdr, outdoor) %>%
  data.frame() %>%
  arrange(desc(is_otdr))

  write_sf(here(paste0("Data/Period_3/out/Test/Hx_", HxRes, ".shp")))
```


```{r}
Hx %>%
  filter(wb_cases > 0)
```


```{r}
TSp_s %>%
  filter(ph_cases != 0)
Mov %>%
  filter(source == 785)
```

Pig cases does not seem to be asociated with movements (very few movements from the affected).\
wild boar cases on those hexagons are not particularly large

```{r}
HxDF %>%
  arrange(desc(wb_cases)) # wild boar cases seem to happen in forest areas
```

```{r}

# ==============================================================================
# Bivariate map with cases, agriculture, and forest info
# ==============================================================================
# ref: https://timogrossenbacher.ch/2019/04/bivariate-maps-with-ggplot2-and-sf/

df = Hx # just for plotting

# create 3 buckets for forest
quantiles_forest <- HxDF %>%
  pull(Forest) %>%
  quantile(probs = seq(0, 1, length.out = 4))

# create 3 buckets for agriculture
quantiles_ag <- HxDF %>%
  pull(Agricultural) %>%
  quantile(probs = seq(0, 1, length.out = 4))

# create color scale that encodes two variables
# red for forest and blue for agriculture
bivariate_color_scale <- tibble(
  "3 - 3" = "#3F2949", 
  "2 - 3" = "#435786",
  "1 - 3" = "#4885C1",
  "3 - 2" = "#77324C",
  "2 - 2" = "#806A8A",
  "1 - 2" = "#89A1C8",
  "3 - 1" = "#AE3A4E",
  "2 - 1" = "#BC7C8F",
  "1 - 1" = "#CABED0" 
) %>%
  gather("group", "fill")
df %<>%
  mutate(
    forest_quantiles = cut(
      Forest,
      breaks = quantiles_forest,
      include.lowest = TRUE
    ),
    ag_quantiles = cut(
      Agricultural,
      breaks = quantiles_ag,
      include.lowest = TRUE
    ),
    group = paste(
      as.numeric(forest_quantiles), "-",
      as.numeric(ag_quantiles)
    )
  ) %>%
  left_join(bivariate_color_scale, by = "group")

map <- ggplot(data = df) +
  geom_sf(aes(fill = fill),
    color = "white",
    size = 0.1) +
  scale_fill_identity() +
  geom_sf(data = TSp_sf, col = "yellow", size = 0.1, alpha = 0.5) +
  theme_void()


# separate the groups
bivariate_color_scale %<>%
  separate(group, into = c("forest", "ag"), sep = " - ") %>%
  mutate(forest = as.integer(forest),
         ag = as.integer(ag))

legend <- ggplot() +
  geom_tile(
    data = bivariate_color_scale,
    mapping = aes(
      x = forest,
      y = ag,
      fill = fill)
  ) +
  scale_fill_identity() +
  labs(x = "Higher forest → ",
       y = "Higher ag →") +
  theme(
    axis.title = element_text(size = 6)
  ) +
  coord_fixed()

ggdraw() +
  draw_plot(map, 0, 0, 1, 1) +
  draw_plot(legend, 0.05, 0.075, 0.2, 0.2, hjust = -3)


```

## Interventions

### Containtment barriers.  

Barriers will be implemented as a rectangle whose diagonal is between points (773676.4, 6347189) and (833676.4, 6437189). We expect that the barriers will be active in 10 days (60 days after the detection of the index case).  

```{r}
# Use the diagonal points to create the square
fenceSp <- cbind(x = c(833676.4, 773676.4, 773676.4, 833676.4, 833676.4), y = c(6347189, 6347189, 6437189, 6437189, 6347189))
# Convert to polygon
fenceSp <- st_polygon(list(fenceSp)) %>%
  st_geometry()
# Set the project CRS
st_crs(fenceSp) <- st_crs(Hx)
# SHow it in a map
Hx %>%
  filter(!is.na(Farms)) %>%
  ggplot() +
  geom_sf() +
  geom_sf(data = fenceSp, alpha = 0.3, col = 'red')

# export the shape:
fences_shp = list.files(here("Data/Period_1/out"),
  pattern = "fenceSp", full.names = TRUE)

if(length(fences_shp) > 0) do.call(file.remove, list(fences_shp))

fenceSp %>% st_write(., here("Data/Period_1/out/fenceSp.shp"))
```

### Increased hunting pressure.  

The goal is to kill about 90% of the alive wild boar within the fenced area, but to test 100%.  
