---
title: "Simulations Output"
output:
  html_document:
    toc: yes
    toc_depth: 4
    theme: cerulean
    highlight: zenburn
---

NOTES:
  - Infected wild boars never reach 0 because the removal of wild boars is only trough hunting pressure which affects equally susceptible and infected.
  - How should we make the re population of pigs?


Baseline:
  - Total culling in farms located < 3km of wild boar detected cases after day 90 (10 days after start of period)

```{r global_options, include = FALSE}

knitr::opts_chunk$set(fig.width=12,
                      fig.height=8,
                      echo=FALSE, warning=FALSE, message=FALSE)

options(DT.options = list(pageLength = 100,
                          dom = 'Bft',
                          filter = "top",
                          buttons = c('copy', 'csv')))

```

# Setting up the workplace

```{r message = FALSE, warning = FALSE}
library(dplyr)
library(ggplot2)
library(ggpubr)
library(sf)
library(here)
library(hrbrthemes)
library(viridis)

out_dir = here("Documentation/Results/Period_3")
if(!dir.exists(out_dir)) dir.create(out_dir, recursive = TRUE)

# ==============================================================================
# FUNCTIONS
# ==============================================================================

# Read Simulations
# ------------------------------------------------------------------------------
ReadSims <- function(dir){
  f <- list.files(dir, full.names = TRUE)
  
  L <- lapply(1:length(f), function(x){
    read.csv(f[x], fileEncoding = 'UTF-8') %>%
      mutate(Sim = x)
    }) %>%
    do.call(rbind, .)
}


# Functions for getting quantiles
# ------------------------------------------------------------------------------
Q25 <- function(sims) quantile(sims, 0.25)
Q75 <- function(sims) quantile(sims, 0.75)


# Function for summarizing the cycles
# ------------------------------------------------------------------------------
CycleSums <- function(sims){
  sims %>%
    dplyr::select(-Sim) %>%
    group_by(cycle) %>%
    summarise_all(.funs = c(Median = median, Q25 = Q25, Q75 = Q75))
}


# Function for the plots
# ------------------------------------------------------------------------------
PlotCycles <- function(sims, var, col, y_lim){
  y_lab = ifelse(grepl("_P", var), "Infected \n pig herds", "Infected \n wild boar")

  p = sims %>%
    CycleSums() %>%
    ggplot(aes(x = cycle)) +
    geom_line(aes(y = eval(parse(text = paste0(var, '_Median')))),
      col = col, lwd = 1) +
    geom_ribbon(aes(
      ymin = eval(parse(text = paste0(var, '_Q25'))),
      ymax = eval(parse(text = paste0(var, '_Q75')))),
      alpha = 0.3, fill = col) +
    theme_minimal() +
    ylab(y_lab) +
    xlab("Days") +
    theme(legend.position = "none",
      axis.title.y = element_text(angle = 0, vjust = 0.5))

  if( !missing(y_lim) ) p = p + ylim(y_lim)

  p
  
}


# Function to convert from long to wide
# ------------------------------------------------------------------------------
## Variable to spread categorical variables
unfold <- function(Dat, Var){
  Dat %>% mutate(N=1) %>% tidyr::spread(eval(parse(text = Var)), N, fill = 0)
}


# Function to make map
# ------------------------------------------------------------------------------
PlotMap = function(info) {
  info =   info %>%
    mutate(Epidemic = ifelse(Epidemic == 0, NA, Epidemic))

  ggplot(info) +
    geom_sf(aes(fill = Epidemic), color = "white", lwd = 0.1) +
    geom_sf(data = st_centroid(subset(Hx, ph_cases > 0)),
      color = "tomato", size = 1) +
    theme_void() +
    labs(fill = "Probability of outbreak") +
    scale_fill_gradient2(
      high = "yellow",
      mid = "darkgoldenrod1", midpoint = 0.25,
      low = "darkblue",
      limits=c(0, 0.5),
      na.value = "snow3")

}

```

# Read in data for various scenarios

```{r}
# # Orig hexgrid shapefile
Hx <- st_read(here("Data/Period_3/out/Hx_5000.shp"), quiet = TRUE) %>%
    mutate(idhex = as.character(idhex))

# scenario 0
S0 <- ReadSims(dir = here("Data/Period_3/Sims/S00/EC/"))
Hx_sim00 <- ReadSims(dir = here("Data/Period_3/Sims/S00/Agents/"))

# scenario 1
S1 <- ReadSims(dir = here("Data/Period_3/Sims/S01/EC/"))
Hx_sim01 <- ReadSims(dir = here("Data/Period_3/Sims/S01/Agents/"))

# scenario 2
S2 <- ReadSims(dir = here("Data/Period_3/Sims/S02/EC/"))
Hx_sim02 <- ReadSims(dir = here("Data/Period_3/Sims/S02/Agents/"))

# scenario 3
S3 <- ReadSims(dir = here("Data/Period_2/Sims/S03/EC/"))
Hx_sim03 <- ReadSims(dir = here("Data/Period_2/Sims/S03/Agents/"))

# scenario 4
S4 <- ReadSims(dir = here("Data/Period_2/Sims/S04/EC/"))
Hx_sim04 <- ReadSims(dir = here("Data/Period_2/Sims/S04/Agents/"))

# scenario 5
S5 <- ReadSims(dir = here("Data/Period_3/Sims/S05/EC/"))
Hx_sim05 <- ReadSims(dir = here("Data/Period_3/Sims/S05/Agents/"))
```

### Variables from the 'EC' folder:

-   *cycle:* time step of the simulation.\
-   *Infected\_P:* Number of infected pig herds.\
-   *Infected\_WB:* Number of infected wild Boars.\
-   *Sim:* Iteration of the simulation.

<br><br>

# Plot of infected domestic pigs and wild boars over time


```{r}
Hx_sim00 %>% count(Disease_status)
Hx_sim00 %>% count(reintroduction)

S0 %>%
  filter(Infected_P == 0) %>%
  group_by(Sim) %>%
  summarise(min(cycle))
```


### Scenario 0: Baseline (fencing, movement restrictions, awareness)

```{r}
# scenario 0
S0 <- ReadSims(dir = here("Data/Period_3/Sims/S00/EC/"))
Hx_sim00 <- ReadSims(dir = here("Data/Period_3/Sims/S00/Agents/"))

S0_pigs <- PlotCycles(S0, var = "Infected_P", col = "pink2")
S0_wb <- PlotCycles(S0, var = "Infected_WB", col = "brown")

p00 = ggarrange(S0_pigs, S0_wb) %>%
  annotate_figure(top = text_grob("No. of infected animals over time\n Scenario 0: Baseline \n",
    color = "darkred", face = "bold", size = 14))
    
p00
```

### Scenario 01: Scenario 0 + hunting pressure

```{r}
# scenario 1
S1 <- ReadSims(dir = here("Data/Period_3/Sims/S01/EC/"))
Hx_sim01 <- ReadSims(dir = here("Data/Period_3/Sims/S01/Agents/"))

S1_pigs <- PlotCycles(S1, var = "Infected_P", col = "pink2")
S1_wb <- PlotCycles(S1, var = "Infected_WB", col = "brown")

p01 = ggarrange(S1_pigs, S1_wb) %>%
  annotate_figure(top = text_grob("No. of infected animals over time\n Scenario 1: Hunting Pressure \n",
    color = "darkred", face = "bold", size = 14))
    
p01

# ggsave(file.path(out_dir, "fig_S1_infected-animals.png"), p)

```

<br><br>

# Maps of infected areas

Variables from the Agents folder:\
- *idhex:* Id of the hexagonal cell.\
- *Epidemic:* Number of times that there was an epidemic on that polygon.\
- *introduction\_ph:* Number of times that an infected pig was introduced to the polygon from other polygon.\
- *introduction\_wb:* Number of times the disease was transmitted from wild boars to a pig herd.

### Scenario 0: Baseline

```{r}
nsims = max(Hx_sim00$Sim)
Hx_sim00_summary <- Hx_sim00 %>%
  mutate(idhex = as.character(idhex)) %>%
  group_by(idhex) %>%
  summarise(reintroduction = sum(reintroduction)) %>%
  mutate(p_reintroduction = reintroduction/nsims) %>% ungroup()

m00 = Hx %>%
  left_join(Hx_sim00_summary, by = 'idhex') %>% 
  ggplot() +
  geom_sf(aes(fill= p_reintroduction)) + 
  theme_void()

p <- ggarrange(p00, m00, nrow = 2)

ggsave(file.path(out_dir, "fig_S0_infected-animals.png"), p)
```

### Scenario 01: Hunting pressure

```{r}
nsims = max(Hx_sim01$Sim)
Hx_sim01_summary <- Hx_sim01 %>%
  mutate(idhex = as.character(idhex)) %>%
  group_by(idhex) %>%
  summarise(reintroduction = sum(reintroduction)) %>%
  mutate(p_reintroduction = reintroduction/nsims) %>% ungroup()

m01 = Hx %>%
  left_join(Hx_sim01_summary, by = 'idhex') %>% 
  ggplot() +
  geom_sf(aes(fill= p_reintroduction)) + 
  theme_void()

p <- ggarrange(p01, m01, nrow = 2)

ggsave(file.path(out_dir, "fig_S0_infected-animals.png"), p)
```

### Scenario 02: Culling of pigs in protection zones

```{r}

Hx_sim02_summary <- Hx_sim02 %>%
  mutate(idhex = as.character(idhex)) %>%
  unfold(., "Disease_status") %>%
  group_by(idhex) %>%
  summarise_at(.vars = c('Epidemic', 'introduction_ph', 'introduction_wb'), .funs = sum)

nsims = max(Hx_sim02$Sim)

m02 = Hx %>%
  left_join(Hx_sim02_summary, by = 'idhex') %>%
  # filter(!is.na(Pop)) %>%
  mutate(Epidemic = ifelse(is.na(cases), Epidemic, 0)/nsims,
    index_case = ifelse(is.na(cases), NA, 1)) %>%
  PlotMap

m02

```

### Scenario 03: Culling of pigs around wild boar positive

```{r}

Hx_sim03_summary <- Hx_sim03 %>%
  mutate(idhex = as.character(idhex)) %>%
  unfold(., "Disease_status") %>%
  group_by(idhex) %>%
  summarise_at(.vars = c('Epidemic', 'introduction_ph', 'introduction_wb'), .funs = sum)

nsims = max(Hx_sim03$Sim)

m03 = Hx %>%
  left_join(Hx_sim03_summary, by = 'idhex') %>%
  # filter(!is.na(Pop)) %>%
  mutate(Epidemic = ifelse(is.na(cases), Epidemic, 0)/nsims,
         index_case = ifelse(is.na(cases), NA, 1)) %>%
  PlotMap

m03

```

### Scenario 04: Increased surveillance

```{r}

Hx_sim04_summary <- Hx_sim04 %>%
  mutate(idhex = as.character(idhex)) %>%
  unfold(., "Disease_status") %>%
  group_by(idhex) %>%
  summarise_at(.vars = c('Epidemic', 'introduction_ph', 'introduction_wb'), .funs = sum)

nsims = max(Hx_sim04$Sim)

m04 = Hx %>%
  left_join(Hx_sim04_summary, by = 'idhex') %>%
  # filter(!is.na(Pop)) %>%
  mutate(Epidemic = ifelse(is.na(cases), Epidemic, 0)/nsims,
         index_case = ifelse(is.na(cases), NA, 1)) %>%
  PlotMap

m04

```

### Scenario 05: Contact tracing

```{r}

Hx_sim05_summary <- Hx_sim05 %>%
  mutate(idhex = as.character(idhex)) %>%
  unfold(., "Disease_status") %>%
  group_by(idhex) %>%
  summarise_at(.vars = c('Epidemic', 'introduction_ph', 'introduction_wb'), .funs = sum)

nsims = max(Hx_sim05$Sim)

m05 = Hx %>%
  left_join(Hx_sim05_summary, by = 'idhex') %>%
  # filter(!is.na(Pop)) %>%
  mutate(Epidemic = ifelse(is.na(cases), Epidemic, 0)/nsims,
         index_case = ifelse(is.na(cases), NA, 1)) %>%
  PlotMap

m05
```



<br><br>

# All scenarios together

```{r}

p_pigs = ggarrange(S0_pigs, S1_pigs, S2_pigs,
  ncol = 4,
  common.legend = TRUE,
  labels = sprintf("Scenario 0%d", 0:3))
p_pigs

p_wb = ggarrange(S0_wb, S1_wb, S2_wb,
  ncol = 4,
  common.legend = TRUE,
  labels = sprintf("Scenario 0%d", 0:3))
p_wb

m_baseline = ggarrange(m00, m01, 
                       common.legend = T, legend = 'right',
                       labels = sprintf('Scenario 0%d', 0:1), heights = 5)

m_pigs = ggarrange(m02, m03, m04, m05,
  ncol = 2, nrow = 2,
  common.legend = TRUE, legend = "right",
  labels = sprintf("Scenario 0%d", 2:5))

m_pigs

ggsave(file.path(out_dir, "fig_map-inf-pigsbaseline-scenarios.png"), m_baseline, height = 5)
ggsave(file.path(out_dir, "fig_map-inf-pigs_all-scenarios.png"), m_pigs)

# ggsave(file.path(out_dir, "fig_inf-pigs_all-scenarios.png"), p_pigs)
# ggsave(file.path(out_dir, "fig_inf-wb_all-scenarios.png"), p_wb)


```

<br><br>

# Summary plot

```{r summary}
S0_I <- S0 %>%
  group_by(Sim) %>%
  summarise(I_P = max(Infected_P)) %>%
  mutate(S = 'Sc 0')

S1_I <- S1 %>%
  group_by(Sim) %>%
  summarise(I_P = max(Infected_P)) %>%
  mutate(S = 'Sc 1')

S2_I <- S2 %>%
  group_by(Sim) %>%
  summarise(I_P = max(Infected_P)) %>%
  mutate(S = 'Sc 2')

ScenariosDF <- rbind(S0_I, S1_I, S2_I)

all_p = ScenariosDF %>%
  ggplot( aes(x = S, y = I_P, fill = S)) +
  geom_boxplot() +
  scale_fill_viridis(discrete = TRUE, alpha=0.6) +
  theme_ipsum() +
  theme(
    legend.position="none",
    plot.title = element_text(size=11),
    axis.title.y = element_text(angle = 0)
  ) +
  xlab("") +
  ylab("No. of \n Infected pig herds")

all_p

# ggsave(file.path(out_dir, "fig_box-plots_all-scenarios.png"), all_p)
```

```{r}
# Export the raw data for submission
# Merge all the scenarios:
SDF <- rbind(S0, S1, S2) %>%
  mutate(Scenario = c(rep("00", 4200), rep("01", 4200), rep('02', 4200)))
# Merge all agents
N_Agents <- 6993
AgentsDF <- rbind(Hx_sim00_summary, Hx_sim01_summary, Hx_sim02_summary) %>%
  mutate(Scenario = c(rep("00", N_Agents), rep("01", N_Agents), rep('02', N_Agents)))

write.csv(SDF, "../../../Data/Period_2/Sims/submission/SDF.csv", row.names = F)
write.csv(AgentsDF, "../../../Data/Period_2/Sims/submission/AgentsDF.csv", row.names = F)
```

```{r}
ScenariosDF %>%
  group_by(S) %>%
  summarise(median(I_P))

## How much does the median decreases depending on the scenarios:
##### Scenario 0
### Scenario 0 vs 1:
(38.97296 - 36.99261) / 38.97296
### Scenario 0 vs 2:
(38.97296 - 29.94144) / 38.97296 # <- the best according to our model
### Scenario 0 vs 3:
(38.97296 - 36.63096) / 38.97296
### Scenario 0 vs 4:
(38.97296 - 30.46799) / 38.97296
### Scenario 0 vs 5:
(38.97296 - 36.13017) / 38.97296

####### Scenario 01
### Scenario 1 vs 2:
(36.99261 - 29.94144) / 36.99261
### Scenario 1 vs 3:
(36.99261 - 36.63096) / 36.99261
### Scenario 1 vs 4:
(36.99261 - 30.46799) / 36.99261
### Scenario 1 vs 5:
(36.99261 - 36.13017) / 36.99261
```
