---
title: "Simulations Output"
output:
  html_document:
    toc: yes
    toc_depth: 4
    theme: cerulean
    highlight: zenburn
---

NOTES:
  - Infected wild boars never reach 0 because the removal of wild boars is only trough hunting pressure which affects equally susceptible and infected.
  - How should we make the re population of pigs?


Baseline:
  - Total culling in farms located < 3km of wild boar detected cases after day 90 (10 days after start of period)

```{r global_options, include = FALSE}
knitr::opts_chunk$set(fig.width=7,
                      fig.height=5,
                      echo=FALSE, warning=FALSE, message=FALSE)
options(DT.options = list(pageLength = 60,
                          dom = 'Bft',
                          filter = "top",
                          buttons = c('copy', 'csv')))
```

<!-- # Setting up the workplace -->

```{r message = FALSE, warning = FALSE}
library(dplyr)
library(ggplot2)
library(ggpubr)
library(sf)
library(here)
library(hrbrthemes)
library(viridis)
out_dir = here("Documentation/Results/Period_3")
if(!dir.exists(out_dir)) dir.create(out_dir, recursive = TRUE)
# ==============================================================================
# FUNCTIONS
# ==============================================================================
# Read Simulations
# ------------------------------------------------------------------------------
ReadSims <- function(dir){
  f <- list.files(dir, full.names = TRUE)
  
  L <- lapply(1:length(f), function(x){
      # print(x)
    read.csv(f[x], fileEncoding = 'UTF-8') %>%
      mutate(Sim = x)
    }) %>%
    do.call(rbind, .)
}
# Functions for getting quantiles
# ------------------------------------------------------------------------------
Q25 <- function(sims) quantile(sims, 0.25)
Q75 <- function(sims) quantile(sims, 0.75)
# Function for summarizing the cycles
# ------------------------------------------------------------------------------
CycleSums <- function(sims){
  sims %>%
    dplyr::select(-Sim) %>%
    group_by(cycle) %>%
    summarise_all(.funs = c(Median = median, Q25 = Q25, Q75 = Q75))
}
# Function for the plots
# ------------------------------------------------------------------------------
PlotCycles <- function(sims, var, col, y_lim){
  y_lab = ifelse(grepl("_P", var), "Infected \n pig herds", "Infected \n wild boar")
  p = sims %>%
    CycleSums() %>%
    ggplot(aes(x = cycle)) +
    geom_line(aes(y = eval(parse(text = paste0(var, '_Median')))),
      col = col, lwd = 1) +
    geom_ribbon(aes(
      ymin = eval(parse(text = paste0(var, '_Q25'))),
      ymax = eval(parse(text = paste0(var, '_Q75')))),
      alpha = 0.3, fill = col) +
    theme_minimal() +
    ylab(y_lab) +
    xlab("Days") +
    theme(legend.position = "none",
      axis.title.y = element_text(angle = 0, vjust = 0.5))
  if( !missing(y_lim) ) p = p + ylim(y_lim)
  p
  
}
# Function to convert from long to wide
# ------------------------------------------------------------------------------
## Variable to spread categorical variables
unfold <- function(Dat, Var){
  Dat %>% mutate(N=1) %>% tidyr::spread(eval(parse(text = Var)), N, fill = 0)
}
# Function to make map
# ------------------------------------------------------------------------------
PlotMap = function(info) {
  info =   info %>%
    mutate(Epidemic = ifelse(Epidemic == 0, NA, Epidemic))
  ggplot(info) +
    geom_sf(aes(fill = Epidemic), color = "white", lwd = 0.1) +
    geom_sf(data = st_centroid(subset(Hx, ph_cases > 0)),
      color = "tomato", size = 1) +
    theme_void() +
    labs(fill = "Probability of outbreak") +
    scale_fill_gradient2(
      high = "yellow",
      mid = "darkgoldenrod1", midpoint = 0.25,
      low = "darkblue",
      limits=c(0, 0.5),
      na.value = "snow3")
}
```

# Data for various scenarios

```{r}
# Orig hexgrid shapefile
Hx <- st_read(here("Data/Period_3/out/Hx_5000.shp"), quiet = TRUE) %>%
    mutate(idhex = as.character(idhex))
# scenario 0
S0 <- ReadSims(dir = here("Data/Period_3/Sims/S00/EC/"))
Hx_sim00 <- ReadSims(dir = here("Data/Period_3/Sims/S00/Agents/"))
# scenario 1
S1 <- ReadSims(dir = here("Data/Period_3/Sims/S01/EC/"))
Hx_sim01 <- ReadSims(dir = here("Data/Period_3/Sims/S01/Agents/"))
# Use the diagonal points to create the square
fenceSp <- cbind(x = c(833676.4, 773676.4, 773676.4, 833676.4, 833676.4), y = c(6347189, 6347189, 6437189, 6437189, 6347189))
# Convert to polygon
fenceSp <- st_polygon(list(fenceSp)) %>%
  st_geometry()
# Set the project CRS
st_crs(fenceSp) <- st_crs(Hx)
fence_buffer = st_buffer(fenceSp, 5*1000)
fence_grid = st_intersection(Hx, fence_buffer)
if(FALSE) {
ggplot() +
  geom_sf() +
    geom_sf(data = Hx, alpha = 0.3, col = 'green', fill = "green") +
    geom_sf(data = fence_grid, alpha = 0.3, col = 'blue')
}
```

## Variables from the 'EC' folder:

-   *cycle:* time step of the simulation.\
-   *Infected\_P:* Number of infected pig herds.\
-   *Infected\_WB:* Number of infected wild Boars.\
-   *Sim:* Iteration of the simulation.

<br><br>


<br><br>

Variables from the Agents folder:\
- *idhex:* Id of the hexagonal cell.\
- *Epidemic:* Number of times that there was an epidemic on that polygon.\
- *introduction\_ph:* Number of times that an infected pig was introduced to the polygon from other polygon.\
- *introduction\_wb:* Number of times the disease was transmitted from wild boars to a pig herd.


# Scenario 0: Baseline (fencing, movement restrictions, awareness)

```{r,fig.height = 6}
# scenario 0
S0 <- ReadSims(dir = here("Data/Period_3/Sims/S00/EC/")) %>%
  distinct()
Hx_sim00 <- ReadSims(dir = here("Data/Period_3/Sims/S00/Agents/")) %>%
  distinct()
S0_pigs <- PlotCycles(S0, var = "Infected_P", col = "pink2")
S0_wb <- PlotCycles(S0, var = "Infected_WB", col = "brown", y_lim = c(0, 1100))
p00 = ggarrange(S0_pigs, S0_wb) %>%
  annotate_figure(top = text_grob("No. of infected animals over time\n Scenario 0: Baseline \n Fencing, movement restrictions, awareness \n",
    color = "darkred", face = "bold", size = 54))
    
nsims = max(Hx_sim00$Sim)
Hx_sim00_summary <- Hx_sim00 %>%
  mutate(idhex = as.character(idhex), 
         reintroduction_b = ifelse(reintroduction > 0 , 1, 0)) %>%
  group_by(idhex) %>%
  summarise(reintroduction = sum(reintroduction_b)) %>%
  mutate(p_reintroduction = reintroduction/nsims) %>% ungroup()

m00_base = Hx %>%
  left_join(Hx_sim00_summary, by = 'idhex') %>% 
  ggplot() +
    geom_sf(aes(fill= p_reintroduction)) +
    geom_sf(data = fenceSp, alpha = 0.3, col = 'blue', fill = NA) +
    theme_void() +
    theme(legend.position = "none")
m00_fence = fence_grid %>%
    left_join(Hx_sim00_summary, by = 'idhex') %>% 
    ggplot() +
    geom_sf(aes(fill= p_reintroduction)) +
    scale_fill_viridis(option="magma", direction = -1) +
    geom_sf(data = fenceSp, alpha = 0.3, col = 'blue', fill = NA) +
    theme_void()
m00 = ggarrange(m00_base, m00_fence) %>%
  annotate_figure(top = text_grob("Map of infected grids within fenced region",
    color = "darkred", face = "bold", size = 54))
p00_all <- ggarrange(p00, m00, nrow = 2)
p00_all
ggsave(file.path(out_dir, "fig_S0_infected-animals.png"), p00_all)
```


<br><br>

# Scenario 01: Scenario 0 + hunting pressure
	
```{r, fig.height = 6}
# scenario 1
S1 <- ReadSims(dir = here("Data/Period_3/Sims/S01/EC/")) %>%
  distinct()
Hx_sim01 <- ReadSims(dir = here("Data/Period_3/Sims/S01/Agents/")) %>%
  distinct()
S1_pigs <- PlotCycles(S1, var = "Infected_P", col = "pink2")
S1_wb <- PlotCycles(S1, var = "Infected_WB", col = "brown")
p01 = ggarrange(S1_pigs, S1_wb) %>%
  annotate_figure(top = text_grob("No. of infected animals over time\n Scenario 1: Hunting Pressure \n Fencing, movement restrictions, awareness, hunting pressure",
    color = "darkred", face = "bold", size = 54))
    
nsims = max(Hx_sim01$Sim)
Hx_sim01_summary <- Hx_sim01 %>%
  mutate(idhex = as.character(idhex), 
         reintroduction_b = ifelse(reintroduction > 0 , 1, 0)) %>%
  group_by(idhex) %>%
  summarise(reintroduction = sum(reintroduction_b)) %>%
  mutate(p_reintroduction = reintroduction/nsims) %>% ungroup()

m01_base = Hx %>%
  left_join(Hx_sim01_summary, by = 'idhex') %>% 
  ggplot() +
    geom_sf(aes(fill= p_reintroduction)) +
    geom_sf(data = fenceSp, alpha = 0.3, col = 'blue', fill = NA) +
    theme_void() +
    theme(legend.position = "none")
m01_fence = fence_grid %>%
    left_join(Hx_sim01_summary, by = 'idhex') %>% 
    ggplot() +
    geom_sf(aes(fill = p_reintroduction)) +
    scale_fill_viridis(option="viridis", direction = -1) +
    geom_sf(data = fenceSp, alpha = 0.3, col = 'blue', fill = NA) +
    theme_void()
m01 = ggarrange(m01_base, m01_fence) %>%
  annotate_figure(top = text_grob("Map of infected grids within fenced region",
    color = "darkred", face = "bold", size = 54))
p01_all <- ggarrange(p01, m01, nrow = 2)
p01_all
ggsave(file.path(out_dir, "fig_S1_infected-animals.png"), p01_all)
```

<br><br>

# Scenario 01: Scenario 0 + hunting pressure
	
```{r, fig.height = 6}
# scenario 1
S2 <- ReadSims(dir = here("Data/Period_3/Sims/S02/EC/")) %>%
  distinct()
Hx_sim02 <- ReadSims(dir = here("Data/Period_3/Sims/S02/Agents/")) %>%
  distinct()
S2_pigs <- PlotCycles(S2, var = "Infected_P", col = "pink2")
S2_wb <- PlotCycles(S2, var = "Infected_WB", col = "brown")
p02 = ggarrange(S2_pigs, S2_wb) %>%
  annotate_figure(top = text_grob("No. of infected animals over time\n Scenario 2: Hunting Pressure \n Fencing, movement restrictions, awareness, hunting pressure",
    color = "darkred", face = "bold", size = 54))
    
nsims = max(Hx_sim02$Sim)
Hx_sim02_summary <- Hx_sim02 %>%
  mutate(idhex = as.character(idhex), 
         reintroduction_b = ifelse(reintroduction > 0 , 1, 0)) %>%
  group_by(idhex) %>%
  summarise(reintroduction = sum(reintroduction_b)) %>%
  mutate(p_reintroduction = reintroduction/nsims) %>% ungroup()

m02_base = Hx %>%
  left_join(Hx_sim02_summary, by = 'idhex') %>% 
  ggplot() +
    geom_sf(aes(fill= p_reintroduction)) +
    geom_sf(data = fenceSp, alpha = 0.3, col = 'blue', fill = NA) +
    theme_void() +
    theme(legend.position = "none")
m02_fence = fence_grid %>%
    left_join(Hx_sim02_summary, by = 'idhex') %>% 
    ggplot() +
    geom_sf(aes(fill = p_reintroduction)) +
    scale_fill_viridis(option="viridis", direction = -1) +
    geom_sf(data = fenceSp, alpha = 0.3, col = 'blue', fill = NA) +
    theme_void()
m02 = ggarrange(m02_base, m02_fence) %>%
  annotate_figure(top = text_grob("Map of infected grids within fenced region",
    color = "darkred", face = "bold", size = 54))
p02_all <- ggarrange(p02, m02, nrow = 2)
p02_all
ggsave(file.path(out_dir, "fig_S2_infected-animals.png"), p02_all)
```


# Misc

```{r, eval = FALSE}
# Export the raw data for submission
# Merge all the scenarios:
SDF <- rbind(S0, S1, S2) %>%
  mutate(Scenario = c(rep("00", 4200), rep("01", 4200), rep('02', 4200)))
# Merge all agents
N_Agents <- 6993
AgentsDF <- rbind(Hx_sim00_summary, Hx_sim01_summary, Hx_sim02_summary) %>%
  mutate(Scenario = c(rep("00", N_Agents), rep("01", N_Agents), rep('02', N_Agents)))
write.csv(SDF, "../../../Data/Period_2/Sims/submission/SDF.csv", row.names = F)
write.csv(AgentsDF, "../../../Data/Period_2/Sims/submission/AgentsDF.csv", row.names = F)
```

```{r, eval = FALSE}
ScenariosDF %>%
  group_by(S) %>%
  summarise(median(I_P))
## How much does the median decreases depending on the scenarios:
##### Scenario 0
### Scenario 0 vs 1:
(38.97296 - 36.99261) / 38.97296
### Scenario 0 vs 2:
(38.97296 - 29.94144) / 38.97296 # <- the best according to our model
### Scenario 0 vs 3:
(38.97296 - 36.63096) / 38.97296
### Scenario 0 vs 4:
(38.97296 - 30.46799) / 38.97296
### Scenario 0 vs 5:
(38.97296 - 36.13017) / 38.97296
####### Scenario 01
### Scenario 1 vs 2:
(36.99261 - 29.94144) / 36.99261
### Scenario 1 vs 3:
(36.99261 - 36.63096) / 36.99261
### Scenario 1 vs 4:
(36.99261 - 30.46799) / 36.99261
### Scenario 1 vs 5:
(36.99261 - 36.13017) / 36.99261