---
title: "Simulations Output"
output:
  html_document:
    toc: true
    toc_depth: 4
    theme: cerulean
    highlight: zenburn
---

```{r global_options, include = FALSE}

knitr::opts_chunk$set(fig.width=12,
                      fig.height=8,
                      echo=FALSE, warning=FALSE, message=FALSE)

options(DT.options = list(pageLength = 100,
                          dom = 'Bft',
                          filter = "top",
                          buttons = c('copy', 'csv')))

```
	
# Setting up the workplace
```{r message = FALSE, warning = FALSE}
library(dplyr)
library(ggplot2)
library(ggpubr)
library(sf)
library(here)
library(hrbrthemes)
library(viridis)

out_dir = here("Results/Period_1")
if(!dir.exists(out_dir)) dir.create(out_dir, recursive = TRUE)

# ==============================================================================
# FUNCTIONS
# ==============================================================================

# Read Simulations
# ------------------------------------------------------------------------------
ReadSims <- function(dir){
  f <- list.files(dir, full.names = TRUE)
  
  L <- lapply(1:length(f), function(x){
    read.csv(f[x], fileEncoding = 'UTF-8') %>%
      mutate(Sim = x)
    }) %>%
    do.call(rbind, .)
}


# Functions for getting quantiles
# ------------------------------------------------------------------------------
Q25 <- function(sims) quantile(sims, 0.25)
Q75 <- function(sims) quantile(sims, 0.75)


# Function for summarizing the cycles
# ------------------------------------------------------------------------------
CycleSums <- function(sims){
  sims %>%
    dplyr::select(-Sim) %>%
    group_by(cycle) %>%
    summarise_all(.funs = c(Median = median, Q25 = Q25, Q75 = Q75))
}


# Function for the plots
# ------------------------------------------------------------------------------
PlotCycles <- function(sims, var, col, y_lim){
  y_lab = ifelse(grepl("_P", var), "Infected \n pigs", "Infected \n wild boar")

  p = sims %>%
    CycleSums() %>%
    ggplot(aes(x = cycle)) +
    geom_line(aes(y = eval(parse(text = paste0(var, '_Median')))),
      col = col, lwd = 1) +
    geom_ribbon(aes(
      ymin = eval(parse(text = paste0(var, '_Q25'))),
      ymax = eval(parse(text = paste0(var, '_Q75')))),
      alpha = 0.3, fill = col) +
    theme_minimal() +
    ylab(y_lab) +
    xlab("Days") +
    theme(legend.position = "none",
      axis.title.y = element_text(angle = 0, vjust = 0.5))

  if( !missing(y_lim) ) p = p + ylim(y_lim)

  p
  
}


# Function to convert from long to wide
# ------------------------------------------------------------------------------
## Variable to spread categorical variables
unfold <- function(Dat, Var){
  Dat %>% mutate(N=1) %>% tidyr::spread(eval(parse(text = Var)), N, fill = 0)
}


# Function to make map
# ------------------------------------------------------------------------------
PlotMap = function(info) {
  info =   info %>%
    mutate(Epidemic = ifelse(Epidemic == 0, NA, Epidemic))

  ggplot(info) +
    geom_sf(aes(fill = Epidemic), color = "white", lwd = 0.1) +
    geom_sf(data = st_centroid(subset(Hx, ph_cass > 0)),
      color = "tomato", size = 1) +
    theme_void() +
    labs(fill = "Probability of outbreak") +
    scale_fill_gradient2(
      high = "yellow",
      mid = "darkgoldenrod1", midpoint = 0.25,
      low = "darkblue",
      limits=c(0, 0.5),
      na.value = "snow3")

}

```

# Read in data for various scenarios
- Scenario 0: Baseline
- Scenario 01: Movement restrictions
- Scenario 02: Movement restrictions and hunting pressure
- Scenario 03: Movement restrictions, hunting pressure and fencing 


```{r}

# Orig hexgrid shapefile
Hx <- st_read(here("Data/Period_1/out/Hx.shp"), quiet = TRUE) %>%
    mutate(idhex = as.character(idhex))

# scenario 0
S0 <- ReadSims(dir = here("Data/Period_1/Sims/S00/EC/"))
Hx_sim00 <- ReadSims(dir = here("Data/Period_1/Sims/S00/Agents/"))

# scenario 1
S1 <- ReadSims(dir = here("Data/Period_1/Sims/S01/EC/"))
Hx_sim01 <- ReadSims(dir = here("Data/Period_1/Sims/S01/Agents/"))

# scenario 2
S2 <- ReadSims(dir = here("Data/Period_1/Sims/S02/EC/"))
Hx_sim02 <- ReadSims(dir = here("Data/Period_1/Sims/S02/Agents/"))

# scenario 3
S3 <- ReadSims(dir = here("Data/Period_1/Sims/S03/EC/"))
Hx_sim03 <- ReadSims(dir = here("Data/Period_1/Sims/S03/Agents/"))

```

### Variables from the 'EC' folder:  
  
  - *cycle:* time step of the simulation.  
  - *Infected_P:* Number of infected pig herds.  
  - *Infected_WB:* Number of infected wild Boars.  
  - *Sim:* Iteration of the simulation.  

<br><br>


# Plot of infected domestic pigs and wild boars over time
### Scenario 0: Baseline

```{r}

S0_pigs <- PlotCycles(S0, var = "Infected_P", col = "pink2", y_lim = c(0, 23))
S0_wb <- PlotCycles(S0, var = "Infected_WB", col = "brown", y_lim = c(400, 750))

p = ggarrange(S0_pigs, S0_wb) %>%
  annotate_figure(top = text_grob("No. of infected animals over time\n Scenario 0: Baseline \n",
    color = "darkred", face = "bold", size = 14))
    
p

ggsave(file.path(out_dir, "fig_S0_infected-animals.png"), p)

```

### Scenario 01: Movement restrictions

```{r}

S1_pigs <- PlotCycles(S1, var = "Infected_P", col = "pink2", y_lim = c(0, 23))
S1_wb <- PlotCycles(S1, var = "Infected_WB", col = "brown", y_lim = c(400, 750))

p = ggarrange(S1_pigs, S1_wb) %>%
  annotate_figure(top = text_grob("No. of infected animals over time\n Scenario 1: Movement restrictions \n",
    color = "darkred", face = "bold", size = 14))
    
p

ggsave(file.path(out_dir, "fig_S1_infected-animals.png"), p)

```

### Scenario 02: Movement restrictions and hunting pressure

```{r}

S2_pigs <- PlotCycles(S2, var = "Infected_P", col = "pink2", y_lim = c(0, 23))
S2_wb <- PlotCycles(S2, var = "Infected_WB", col = "brown", y_lim = c(400, 750))

p = ggarrange(S2_pigs, S2_wb) %>%
  annotate_figure(top = text_grob("No. of infected animals over time\n Scenario 02: Movement restrictions and hunting pressure \n",
    color = "darkred", face = "bold", size = 14))
    
p

ggsave(file.path(out_dir, "fig_S2_infected-animals.png"), p)

```

### Scenario 03: Movement restrictions, hunting pressure and fencing

```{r}

S3_pigs <- PlotCycles(S3, var = "Infected_P", col = "pink2", y_lim = c(0, 23))
S3_wb <- PlotCycles(S3, var = "Infected_WB", col = "brown", y_lim = c(400, 750))

p = ggarrange(S3_pigs, S3_wb) %>%
  annotate_figure(top = text_grob("No. of infected animals over time\n Scenario 03: Movement restrictions, hunting pressure and fencing \n",
    color = "darkred", face = "bold", size = 14))
    
p

ggsave(file.path(out_dir, "fig_S3_infected-animals.png"), p)

```

<br><br>

# Maps of infected areas 
  
Variables from the Agents folder:  
  - *idhex:* Id of the hexagonal cell.  
  - *Epidemic:* Number of times that there was an epidemic on that polygon.  
  - *introduction_ph:* Number of times that an infected pig was introduced to the polygon from other polygon.  
  - *introduction_wb:* Number of times the disease was transmitted from wild boars to a pig herd.  
    

### Scenario 0: Baseline
```{r}

Hx_sim00_summary <- Hx_sim00 %>%
  mutate(idhex = as.character(idhex)) %>%
  unfold(., "Disease_status") %>%
  group_by(idhex) %>%
  summarise_at(.vars = c('Epidemic', 'introduction_ph', 'introduction_wb'), .funs = sum)

nsims = max(Hx_sim00$Sim)

m00 = Hx %>%
  left_join(Hx_sim00_summary, by = 'idhex') %>%
  # filter(!is.na(Pop)) %>%
  mutate(Epidemic = ifelse(is.na(cases), Epidemic, 0)/nsims,
    index_case = ifelse(is.na(cases), NA, 1)) %>%
  PlotMap

m00

```

### Scenario 01: Movement restrictions
```{r}

Hx_sim01_summary <- Hx_sim01 %>%
  mutate(idhex = as.character(idhex)) %>%
  unfold(., "Disease_status") %>%
  group_by(idhex) %>%
  summarise_at(.vars = c('Epidemic', 'introduction_ph', 'introduction_wb'), .funs = sum)

nsims = max(Hx_sim01$Sim)

m01 = Hx %>%
  left_join(Hx_sim01_summary, by = 'idhex') %>%
  # filter(!is.na(Pop)) %>%
  mutate(Epidemic = ifelse(is.na(cases), Epidemic, 0)/nsims,
         index_case = ifelse(is.na(cases), NA, 1)) %>%
  PlotMap

m01

```

### Scenario 02: Movement restrictions and hunting pressure
```{r}

Hx_sim02_summary <- Hx_sim02 %>%
  mutate(idhex = as.character(idhex)) %>%
  unfold(., "Disease_status") %>%
  group_by(idhex) %>%
  summarise_at(.vars = c('Epidemic', 'introduction_ph', 'introduction_wb'), .funs = sum)

nsims = max(Hx_sim02$Sim)

m02 = Hx %>%
  left_join(Hx_sim02_summary, by = 'idhex') %>%
  # filter(!is.na(Pop)) %>%
  mutate(Epidemic = ifelse(is.na(cases), Epidemic, 0)/nsims,
    index_case = ifelse(is.na(cases), NA, 1)) %>%
  PlotMap

m02

```

### Scenario 03: Movement restrictions, hunting pressure and fencing
```{r}

Hx_sim03_summary <- Hx_sim03 %>%
  mutate(idhex = as.character(idhex)) %>%
  unfold(., "Disease_status") %>%
  group_by(idhex) %>%
  summarise_at(.vars = c('Epidemic', 'introduction_ph', 'introduction_wb'), .funs = sum)

nsims = max(Hx_sim03$Sim)

m03 = Hx %>%
  left_join(Hx_sim03_summary, by = 'idhex') %>%
  # filter(!is.na(Pop)) %>%
  mutate(Epidemic = ifelse(is.na(cases), Epidemic, 0)/nsims,
         index_case = ifelse(is.na(cases), NA, 1)) %>%
  PlotMap

m03

```

<br><br>

# All scenarios together

```{r}

p_pigs = ggarrange(S0_pigs, S1_pigs, S2_pigs, S3_pigs,
  ncol = 4,
  common.legend = TRUE,
  labels = sprintf("Scenario 0%d", 0:3))
p_pigs

p_wb = ggarrange(S0_wb, S1_wb, S2_wb, S3_wb,
  ncol = 4,
  common.legend = TRUE,
  labels = sprintf("Scenario 0%d", 0:3))
p_wb

m_pigs = ggarrange(m00, m01, m02, m03,
  ncol = 2, nrow = 2,
  common.legend = TRUE, legend = "right",
  labels = sprintf("Scenario 0%d", 0:3))
m_pigs

ggsave(file.path(out_dir, "fig_inf-pigs_all-scenarios.png"), p_pigs)
ggsave(file.path(out_dir, "fig_inf-wb_all-scenarios.png"), p_wb)
ggsave(file.path(out_dir, "fig_map-inf-pigs_all-scenarios.png"), m_pigs)

```

<br><br>

# Summary plot

```{r summary}

S0_I <- S0 %>%
  group_by(Sim) %>%
  summarise(I_P = max(Infected_P)) %>%
  mutate(S = 'Scenario 0')

S1_I <- S1 %>%
  group_by(Sim) %>%
  summarise(I_P = max(Infected_P)) %>%
  mutate(S = 'Scenario 1')

S2_I <- S2 %>%
  group_by(Sim) %>%
  summarise(I_P = max(Infected_P)) %>%
  mutate(S = 'Scenario 2')

S3_I <- S3 %>%
  group_by(Sim) %>%
  summarise(I_P = max(Infected_P)) %>%
  mutate(S = 'Scenario 3')

ScenariosDF <- rbind(S0_I, S1_I, S2_I, S3_I)

all_p = ScenariosDF %>%
  ggplot( aes(x = S, y = I_P, fill = S)) +
  geom_boxplot() +
  scale_fill_viridis(discrete = TRUE, alpha=0.6) +
  theme_ipsum() +
  theme(
    legend.position="none",
    plot.title = element_text(size=11),
    axis.title.y = element_text(angle = 0)
  ) +
  xlab("") +
  ylab("No. of \n Infected pigs")

all_p

ggsave(file.path(out_dir, "fig_box-plots_all-scenarios.png"), all_p)

```

```{r}
ScenariosDF %>%
  group_by(S) %>%
  summarise(median(I_P))

## How much does the median decreases depending on the scenarios:
### Scenario 0 vs 2:
(16.9092 - 12.9955) / 16.9092
### Scenario 0 vs 3:
(16.9092 - 11.8742) / 16.9092

```
